Multidimensional signals and analytic flexibility: Estimating degrees of freedom in human speech analyses

### 2023-01-28 RR_manuscript/RR.Rmd
removed reference to "orange" in fig 3

While the majority of model estimates and their uncertainty after shrinkage (in black) yields inconclusive results (i.e. are compatible with a point null hypothesis), there are `r compelling_count_nest[[1]] + compelling_count_nest[[3]]` model estimates for which the 95\% credible interval does not contain zero (in orange, `r round((compelling_results_nest[[1,1]] + compelling_results_nest[[3,1]]), 2) * 100`\%).

<!-- FIGURE -->
(ref:plot-meta1) Standardized effect sizes across all critical coefficients provided by the teams. Raw estimates are displayed in grey. Estimates after shrinkage as provided by the meta-analytic model are displayed in black/orange.

>>>>

While the majority of model estimates and their uncertainty after shrinkage yields inconclusive results (i.e. are compatible with a point null hypothesis), there are `r compelling_count_nest[[1]] + compelling_count_nest[[3]]` model estimates for which the 95\% credible interval does not contain zero (`r round((compelling_results_nest[[1,1]] + compelling_results_nest[[3,1]]), 2) * 100`\%).

<!-- FIGURE -->
(ref:plot-meta1) Standardized effect sizes across all critical coefficients provided by the teams. Raw estimates are displayed in grey. Estimates after shrinkage as provided by the meta-analytic model are displayed in black.
